\documentclass[]{resume-openfont}

\pagestyle{fancy}
\resetHeaderAndFooter

%--------------------------------------------------------------
% Convenience command - make it easy to fill template

% Create job position command. Parameters: company, position, location, when
\newcommand{\resumeHeading}[4]{\runsubsection{\uppercase{#1}}\descript{ | #2}\hfill\location{#3 | #4}\fakeNewLine}

% Create education heading. Parameters: Name, degree, location, when
\newcommand{\educationHeading}[4]{\runsubsection{#1}\hspace*{\fill}  \location{#3 | #4}\\
\descript{#2}\fakeNewLine}

% Create project heading. Parameters: Name, link, Tech stack
\newcommand{\projectHeading}[3]{\Project{#1}{#2}
\descript{#3}\\}

\newcommand{\projectHeadingWithDate}[4]{\Project{#1}{#2}
\descript{#3 | #4}\\}

% Parameters: courses
\newcommand{\courseWork}[1]{\textbf{Coursework:} #1}

% Parameters: courses
\newcommand{\teacherAssistant}[1]{\textbf{Teacher Assistant (TA):} #1}
 
%--------------------------------------------------------------
\begin{document}

%--------------------------------------------------------------
%     Profile
%--------------------------------------------------------------
\newcommand{\yourName}{Arpon Kapuria}
% How you want it to show up on the resume
\newcommand{\yourWebsite}{website.com}
% vs how you want it to show up. If it's the same you can just replace "\yourWebsiteLink" with "yourWebsite"
\newcommand{\yourWebsiteLink}{https://website.com}
\newcommand{\yourEmail}{arpkapuria@gmail.com}
\newcommand{\yourPhone}{+91 8015845227}
\newcommand{\githubUserName}{aaaaarrp}
\newcommand{\linkedInUserName}{arponkapuria}

% An alternate profile section 
% \alignProfileTable
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%     \ralewayBold{\href{\yourWebsiteLink}{\Large \yourName}} & 
%     Email : \href{mailto:\yourEmail}{\yourEmail}
%     \\
%     \href{https://github.com/\githubUserName}{GitHub://\githubUserName} & 
%     Mobile : \yourPhone
%     \\
%     \href{https://www.linkedin.com/in/\linkedInUserName}{LinkedIn://\linkedInUserName} & Website : \href{\yourWebsiteLink}{\yourWebsite}
%     \\
% \end{tabular*}

\begin{center}
    \Huge \scshape \latoRegular{\yourName} \\ \vspace{1pt}
    \small \href{mailto:\yourEmail}{\underline{\yourEmail}}  $|$  \yourPhone $|$ 
    \href{https://www.linkedin.com/in/\linkedInUserName}{\underline{linkedIn/\linkedInUserName}} $|$
    \href{https://github.com/\githubUserName}{\underline{github/\githubUserName}} 
    % $|$ \href{\yourWebsiteLink}{\underline{\yourWebsite}}
\end{center}

%--------------------------------------------------------------
%     Education
%--------------------------------------------------------------
\section{Education}
% Put school first and degree second if your school is reputable
\educationHeading{B.Tech in Computer Science and Engineering }{National Institute of Technology, Tiruchirappalli}{Tamil Nadu, IN}{December 2020 - Present}

\ExpectedGraduationDate{Expected Graduation Date: July 2024}
% \courseWork{Data Structures and Algorithms; Operating Systems;  Computer Security; Software Testing; Advanced Networking; Big Data Analytics}
\sectionsep

%--------------------------------------------------------------
%     Experience
%--------------------------------------------------------------
\section{Experience}
\resumeHeading{Mir Zahid Art School}{Art Instructor}{Kushtia, BD}{June 2018 – November 2018}
\begin{bullets}
    \item Taught pre-teen students on weekend art classes. Helped around 50 students in developing pastel drawing skill.
\end{bullets}
\sectionsep


%--------------------------------------------------------------
%     Projects
%--------------------------------------------------------------
\section{Projects}
\projectHeading{Smart Home Management Suite}{}{September 2022 - Present}
\begin{bullets}
    \item Developed a flutter app to manage smart home automation across 4 clusters, each having 15 homes in Assam, India.\\
    \item Created both admin portal and user side for controlling electronic devices such as lights, fans, etc.\\
    \item Used the MQTT server for IoT communication and integrated flutter frontend with API integrated in Django by another teammate.\\
    \item Parsed energy metre data to generate bills and made summary reports in the admin dashboard.\\
\end{bullets}
\sectionsep
  
\projectHeading{Malicious Website Detection Using Machine Learning}{}{October 2022 - November 2022}
\begin{bullets}
    \item Implemented a machine-learning model with MLP algorithm to detect malicious websites using tensorflow.
    \item Built a chrome extension to extract the features from the webpage to test the website against the trained model to classify if it is malicious or not.
    \item Added a feature in the extension to get user feedback, in case the classification is wrong and used a continual learning approach to store the data and retrain the model daily to improve the model’s performance.
\end{bullets}
\sectionsep

\projectHeading{Fruit Ninja Clone}{}{October 2022}
\begin{bullets}
    \item Made this 2D game with Unity and C#. It is a clone of the famous mobile game Fruit Ninja developed by Halfbrick Studios.
    \item In Fruit Ninja, the player slices fruits with a blade controlled via the touch screen. In my clone version, Instead of touching, one can use a mouse to move the blade to slice the fruits. We can see the points on the screen after every slicing.
\end{bullets}
\sectionsep

% Example using bullets and dates 
% \projectHeadingWithDate{Hogwart\textquotesingle{}s Library Management System}{https://github.com/Aarif123456/hogwartslibrary}{PHP, JavaScript, HTML, CSS, MySQL}{Aug 2019}
% \begin{bullets}
%     \item A full-stack library management system, where users can manage books and holds on their accounts. Users can search the library\textquotesingle{}s catalogue, which has every book mentioned in the Harry Potter series. The system distinguishes between 4 users. For examples, librarians who can also check or return books on behalf of users.\\
% \end{bullets}
% \sectionsep
  

%--------------------------------------------------------------
%     Skills
%--------------------------------------------------------------
\section{Skills}
\begin{skillList}
    \singleItem{Languages:}{C, C++, Python, Dart} \\
    \singleItem{Web Development:}{JavaScript, HTML, CSS} \\
    \singleItem{Database:}{MySQL} \\
    \singleItem{Framework:}{Flutter, Tailwind CSS, TensorFlow} \\
    \singleItem{Game Development:}{Unity, C\#} \\
    \singleItem{Others:}{Git, Docker, MS Office, \LaTeX}
\end{skillList}
\sectionsep



%--------------------------------------------------------------
%     Achievements
%--------------------------------------------------------------

\section{Achievements}
\begin{bullets}
    \item \textbf{2020} Indian Council for Cultural Relationship (ICCR) scholarship awardee – selected as one of the 200 students receiving this scholarship from Bangladesh by the Govt. of India.
    \item \textbf{2017} Merit Order Scholarship from the Chamber of Commerce, Kushtia, Bangladesh because of the excellent performance in 10th board exam.
    \item \textbf{2015} Received General Grade Scholarship from the Govt. of Bangladesh in the 8th board exam.
    \item Won multiple prizes in art competitions organized by: \textbf{Bangladesh Udichi Shilpigoshthi}, \textbf{Zilla Shilpokola Academy, Kushtia}, \textbf{Bangladesh Shishu Academy} and \textbf{Inter-School} cultural fests in Bangladesh.
\end{bullets}
\sectionsep

% A more concise alternate 
% \begin{skillList}
%     \doubleItem{Languages:}{Java, C++, Python, C\#, PHP, Prolog, Bash, C, Racket}%
%     {Databases:}{SQL, MongoDB, Neo4j, DynamoDB}
%     \\
%     \doubleItem{Web Development:}{JavaScript, TypeScript, React, HTML/CSS}
%     {Technology:}{Git, AWS, GCP, Azure, Docker, \LaTeX}%
% \end{skillList}
\end{document}